Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-02 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Update footnotes...

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtract intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}.
The left-end of the interval-valued probability measure is a special
case of game~\cite{Shapley1965}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
we have 
\[
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
\]
where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
for all $i$.
\end{itemize}
In order to understand this definition, we tear the last condition
apart and provide an equivalent definition of interval-valued probability
measures.

@@

\begin{thm}{[}Shapley~\cite{Shapley1965,GilboaSchmeidler1994}{]}\label{thm:Shapley}
Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}

@@

\begin{example}{[}One-qubit quantum probability space{]} Consider
a one-qubit Hilbert space with states $\ket{\phi}$, which can be
expressed as a linear combination of $\ket{0}$ and $\ket{1}$, i.e.,
$\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$ such that $|\alpha|^{2}+|\beta|^{2}=1$,
$\alpha,\beta\in\C$. The set of events associated with this Hilbert
space consists of all projection operators. Each event is interpreted
as a possible post-measurement state of a quantum system in current
state $\ket{\phi}$. For example, the event $\proj{0}$ indicates
that the post-measurement state will be $\ket{0}$; the event $\proj{1}$
indicates that the post-measurement state will be $\ket{1}$; the
event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
indicates that the post-measurement state will be $\ket{\ps}$; the
event $\mathbb{1}=\proj{0}\tensor*[_{\mathscr{O}}]{+}{}\proj{1}$
indicates that the post-measurement state will be a linear combination
of $\ket{0}$ and $\ket{1}$; and the empty event $\mathbb{0}$ states
that the post-measurement state will be the empty state. As in the
classical case, a probability measure is a function that maps events
to $[0,1]$. Here is a partial specification of a possible probability
measure: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
\]
Note that, similarly to the classical case, the probability of $\mathbb{1}$
is 1 and the probability of collections of orthogonal events (e.g.,
$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
is however not even a valid event. In the classical example, we argued
that each probability measure is uniquely determined by two actual
coins. A similar (but much more subtle) argument is valid also in
the quantum case. By postulates of quantum mechanics and Gleason's
theorem, it turns out that for large enough quantum systems, each
probability measure is uniquely determined by an actual quantum state.
\qed\end{example}

@@

\begin{thm}{[}Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}{]}\label{cor:Gleason's}In
a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, there exists an unique mixed
state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{thm}

>>>>

As motivated above, an event $E_{1}$ may have an interval of probability
$[l_{1},r_{1}]$. Assume that another disjoint event $E_{2}$ has
interval probability $[l_{2},r_{2}]$, what is the interval probability
of the event $E_{1}\cup E_{2}$? The answer is somewhat subtle: although
it is possible to use the sum of the intervals $[l_{1}+l_{2},r_{1}+r_{2}]$
as the combined probability, one can do find a much tighter interval
if information \emph{against} the event (i.e., information about the
complement event) is also taken into consideration. Formally, for
a general event $E$ with probability $[l,r]$, the evidence that
contradicts $E$ is an evidence supporting the complement of $E$.
The complement of $E$ must therefore have probability $\left[1-r,1-l\right]$
which we abbreviate $\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\left[l,r\right]$,
where the preposing $\mathscr{I}$ specifies we subtract intervals.
Given a collection of intervals $\mathscr{I}$, an $\mathscr{I}$\textendash interval-valued
probability measure is a function $\bar{\mu}:\events\rightarrow\mathscr{I}$
such that~\cite{JamisonLodwick2004}:\footnote{The right-end of the interval-valued probability measure is a special
case of (sub-additive) capacity~\cite{Choquet1954,Graf1980,Goodman2013}
or outer measure~\cite{Folland2013}. The left-end of the interval-valued
probability measure is a special case of game~\cite{Shapley1965}.} 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$, 
\item $\bar{\mu}(\Omega)=[1,1]$, 
\item for every collection of pairwise disjoint events $\left\{ E_{i}\right\} _{i=1}^{N},\left\{ E_{i}'\right\} _{i=1}^{N'}\subseteq\events$
with $\Omega=\left(\bigcup_{i=1}^{N}E_{i}\right)\bigcup\left(\bigcup_{i=1}^{N'}E_{i}'\right)$,
we have 
\[
\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\left[\max\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum r_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum l_{i}\right\} ,\min\left\{ 1-\sideset{_{\mathbb{R}}}{_{i=1}^{N'}}\sum l_{i}',\sideset{_{\mathbb{R}}}{_{i=1}^{N}}\sum r_{i}\right\} \right]\textrm{ ,}
\]
where $\bar{\mu}\left(E_{i}\right)=[l_{i},r_{i}]$ and $\bar{\mu}\left(E_{i}'\right)=[l_{i}',r_{i}']$
for all $i$.
\end{itemize}
In order to understand this definition, we tear the last condition
apart and provide an equivalent definition of interval-valued probability
measures.

@@

\begin{thm}[Shapley~\cite{Shapley1965,GilboaSchmeidler1994}]\label{thm:Shapley}
Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}

@@

\begin{example}[One-qubit quantum probability space] Consider
a one-qubit Hilbert space with states $\ket{\phi}$, which can be
expressed as a linear combination of $\ket{0}$ and $\ket{1}$, i.e.,
$\ket{\phi}=\alpha\ket{0}+\beta\ket{1}$ such that $|\alpha|^{2}+|\beta|^{2}=1$,
$\alpha,\beta\in\C$. The set of events associated with this Hilbert
space consists of all projection operators. Each event is interpreted
as a possible post-measurement state of a quantum system in current
state $\ket{\phi}$. For example, the event $\proj{0}$ indicates
that the post-measurement state will be $\ket{0}$; the event $\proj{1}$
indicates that the post-measurement state will be $\ket{1}$; the
event $\proj{\ps}$ where $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
indicates that the post-measurement state will be $\ket{\ps}$; the
event $\mathbb{1}=\proj{0}\tensor*[_{\mathscr{O}}]{+}{}\proj{1}$
indicates that the post-measurement state will be a linear combination
of $\ket{0}$ and $\ket{1}$; and the empty event $\mathbb{0}$ states
that the post-measurement state will be the empty state. As in the
classical case, a probability measure is a function that maps events
to $[0,1]$. Here is a partial specification of a possible probability
measure: 
\[
\begin{array}{rcl}
\mu\left(\mathbb{0}\right)=0,\quad\mu\left(\mathbb{1}\right)=1,\quad\mu\left(\proj{0}\right)=1,\quad\mu\left(\proj{1}\right)=0,\quad\mu\left(\proj{\ps}\right)=1/2,\quad\ldots\end{array}
\]
Note that, similarly to the classical case, the probability of $\mathbb{1}$
is 1 and the probability of collections of orthogonal events (e.g.,
$\proj{0}+\proj{1}$) is the sum of the individual probabilities.
A collection of non-orthogonal events (e.g., $\proj{0}$ and $\proj{\ps}$)
is however not even a valid event. In the classical example, we argued
that each probability measure is uniquely determined by two actual
coins. A similar (but much more subtle) argument is valid also in
the quantum case. By postulates of quantum mechanics and Gleason's
theorem, it turns out that for large enough quantum systems, each
probability measure is uniquely determined by an actual quantum state.
\qed\end{example}

@@

\begin{thm}[Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}]\label{cor:Gleason's}In
a Hilbert space $\Hilb$ of dimension $d\geq3$, given a quantum probability
measure~$\mu:\events\rightarrow[0,1]$, there exists an unique mixed
state~$\rho$ such that $\mu=\mu_{\rho}^{B}$.\end{thm}
